The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley \revision{Radio Observatory} Long Wavelength Array

### 2018-04-25 paper.tex
update lwa1 comparison and ionospheric text

\subsection{Ionospheric Conditions}

@@

In order to account for propagation effects through the ionosphere, direction-dependent calibration
and peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S} must be used.  Direction-dependent
calibration allows the per-antenna amplitude and phase towards a bright astronomical source to be
free parameters. In the dataset used in this paper, scintillation and refractive-offset events on
the timescale of a single integration (13 seconds) are observed (Figure~\ref{fig:scintillation}).
Therefore, the direction dependent calibration changes on these timescales, and we must solve for
one set of complex gains per source per integration.

The largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular scale of Cyg~A is
$\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at 73~MHz, the OVRO-LWA
marginally resolves both sources. A resolved source model is needed for both sources. We fit a
self-consistent resolved source model to each source. This is performed by minimizing the variance
within an aperture located on each source after peeling. By phasing up a large number of
integrations before imaging (at least 1 hour), it is possible to smear out the contribution of the
rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx) \citep{nlopt, sbplx}
to vary the parameters in a source model until the variance within the aperture is minimized. Cyg~A
is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian components. Armed with
these  source models, both sources can be peeled from the dataset to the required dynamic range.

@@

The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced nine maps of the sky
between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
work.  A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In
this figure, the LLFSS maps are filtered to remove the monopole and all modes with $m=0$. The
OVRO-LWA maps are interpolated in frequency and blurred to match the angular resolution of the
corresponding LLFSS map. This comparison uncovered a $\sim45$~arcmin rotation in the LLFSS maps
about the NCP, which is corrected in Figure~\ref{fig:lwa1-comparison}.  At 60~MHz, the agreement is
generally better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.
Typically the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off
the galactic plane relative to the LLFSS.

>>>>

\subsection{Ionospheric Conditions}\label{sec:ionosphere-conditions}

@@

\revision{To achieve this dynamic range at low frequencies, it is important to account for
propagation effects through the ionosphere. In the weak scattering regime ($b_\text{max} \ll 2\pi
r_\text{diff}$, where $b_\text{max}$ is the maximum baseline length, and $r_\text{diff}$ is the
diffractive scale of the ionosphere), fluctuations within the ionosphere contribute amplitude and
phase scintillations that can be described by a direction-dependent complex-gain calibration. This
justifies the use of ``peeling'', which incorporates a direction-dependent calibration to subtract
sources in the presence of ionospheric scintillation.  \citep[eg.][]{2008ISTSP...2..707M,
2015MNRAS.449.2668S}.}

\revision{In the strong scattering regime ($b_\text{max} \gtrsim 2\pi r_\text{diff}$), the image of
a point source can ``break apart'' into multiple images or speckles \citep{2015MNRAS.453..925V}.
Attempting to peel a source in the strong scattering regime will lead to source subtraction
artifacts in the final sky map.  \citet{2016RaSc...51..927M} measured that from the location of
LOFAR at 150 MHz, the diffractive scale of the ionosphere is $>5$ km 90\% of the time. This implies
that at 73 MHz, the diffractive scale is typically $>2$ km, and at 36 MHz, the diffractive scale is
typically $>1$ km. The maximum baseline length of the OVRO-LWA is $\sim 1.5$ km, and therefore we do
not generally expect to see strong scattering from the ionosphere.  Furthermore, ionospheric
conditions during the observing period were mild (see \S\ref{sec:ionosphere-conditions}), but we
still observe scintillation and refractive-offset events on the timescale of a single integration
(13 seconds, see Figure~\ref{fig:scintillation}). Consequently we peeled Cyg~A and Cas~A from the
dataset using a new solution for each integration.}

\revision{In addition, the largest angular scale of Cas~A is $\sim$8~arcmin, and the largest angular
scale of Cyg~A is $\sim$2~arcmin. With a $\sim10$~arcmin resolution on its longest baselines at
73~MHz, the OVRO-LWA marginally resolves both sources. A resolved source model is needed for both
sources. We fit a self-consistent resolved source model to each source. This is performed by
minimizing the variance within an aperture located on each source after peeling. By phasing up a
large number of integrations before imaging (at least 1 hour), it is possible to smear out the
contribution of the rest of the sky.  We then use a non-linear optimization routine (NLopt Sbplx)
\citep{nlopt, sbplx} to vary the parameters in a source model until the variance within the aperture
is minimized. Cyg~A is modeled with 2 Gaussian components, while Cas~A is modeled with 3~Gaussian
components.  Ultimately, these multi-component models are used to peel Cyg~A and Cas~A, but residual
errors from this model and from the ionosphere (particularly while these sources are at low
elevations) contribute residual artifacts that are largely localized to within 1$^\circ$ of each
source.}

@@

The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced nine maps of the sky
between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
work. \revision{Initial comparisons with the LLFSS helped characterize a systematic rotation in the
LWA1's antenna positions. After phase-calibration, this manifested itself as a systematic rotation
and translation in the snapshot images that were mosaicked to form the final sky map. This
systematic error has been corrected in the comparisons presented here and in the latest version of
the LLFSS\footnote{
    Available for download at: \url{http://lda10g.alliance.unm.edu/LWA1LowFrequencySkySurvey/}
}.}

\revision{A direct comparison with these updated LLFSS maps can be seen in
Figure~\ref{fig:lwa1-comparison}.  In this figure, the LLFSS maps are filtered to remove the
monopole and all modes with $m=0$. The OVRO-LWA maps are interpolated in frequency and blurred to
match the angular resolution of the corresponding LLFSS map.  At 60~MHz, the agreement is generally
better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.  Typically
the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off the
galactic plane relative to the LLFSS.}
